Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
adding some of the citations

Software debugging is difficult. In particular, the task of locating the faulty
code (\ie{}, fault localization) is particularly challenging. For that reason,
countless automated techniques have been proposed in the past to reduce the cost
of fault localization. \Rui{cite my TSE survey paper.}

@@

Model-based software diagnosis (MBSD) \Rui{cite de kleer, reiter} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
some works of Wotawa}, a technique that traces back statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

>>>>

Software debugging is difficult. In particular, the task of locating the faulty
code (\ie{}, fault localization) is particularly challenging. For that reason,
countless automated techniques have been proposed in the past to reduce the cost
of fault localization~\cite{7390282}.

@@

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as wel as some work~\cite{Perez:2018:LQR:3304889.3304927}\Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
some works of Wotawa}, a technique that traces back statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code . Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
